\paragraph{Personality Questionnaire}
Pending Ethics Committee approval, during sign-up the user will be asked to complete a short questionnaire about their personality. This questionnaire will be optional, however may provide some insights into the types of users for whom game mechanics are most effective. The following questions may be included:

\begin{enumerate}
    \item I tend to leave tasks until the last minute.
    \item I enjoy challenges
    \item I enjoy learning
    \item I am competitive
\end{enumerate}

The users will be asked to rate each question on a 5-point Likert scale \cite{rensis_likert_technique_1932} with the following options:
\begin{enumerate}
	\item Strongly Disagree
	\item Disagree
	\item Neither Agree nor Disagree
	\item Agree
	\item Strongly Agree
\end{enumerate}

\paragraph{User Ratings}
Users will be asked to quickly rate their feelings about the system to gauge subjective feelings. To encourage users to complete the rating - this will only be asked occasionally and will be very short. The following questions may be included:

\begin{enumerate}
    \item I feel I am learning a lot with \SoftName.
    \item I look forward to using \SoftName\
    \item I feel inspired to learn with \SoftName\
\end{enumerate}

The users will be asked to rate each question on a 5-point Likert scale as described in previous section.

\paragraph{Activity Logging}
All activity on the system will be logged including timestamping when challenges are started and 
completed, timestamping transitions between questions on each challenge, and time that 
the user is considered idle. These metrics allow for later investigation into 
and quantitative analysis of the user's engagement with the system.
