\subsubsection{Planning and Proposal}
(5 weeks)
The initial stage is the project planning for which the deliverable is this document.

\subsubsection{Requirements}
(1 week)
Following planning, a requirements document should be prepared which details the scope of the project in more detail. This ensures a clear understanding of the technical work required to complete the project.

\subsubsection{UI Design and Layouts}
(2 Weeks)
With the requirements in place, the layout of the user interface (UI) should
be prepared before any coding is completed. Deliverables at this stage include:
\begin{itemize}
	\item Wireframes of all user-facing screens 
	\item Storyboards detailing the flow of user interaction
\end{itemize}

\subsubsection{Onboarding Teaching Staff}
(2 Weeks)
As the project requires a class of students and vocabulary lists to complement
the class, teaching staff will need to be contacted for their willingness to
participate in the project. The potential benefits to student of higher vocabulary
retention due to the use of the system should be explained.

\subsubsection{Ethics Committee Approval}
(1 Week)
As this project involves humans, the methods must be approved by the University
Ethics Committee. The approval process can take between a week and several
months.

\subsubsection{Produce Vocabulary Lists}
(1 Week)
Lists of vocabulary will need to be produced which complement the classes.
Depending upon the class, the teaching staff may have already produced a
list of vocabulary, although this is unlikely to be electronic in which case
the vocabulary will need to be entered into a computer readable format. In
other classes, the vocabulary may need to be sourced from a textbook. In either
case it is expected that this data entry will take under a week.

\subsubsection{Working Software Prototype}
(4 Weeks)
A working software prototype must be prepared in time for the beginning of
Semester 2 including the ability for the students to sign up and begin using
the system. All activity/data logging must also be in place.

\subsubsection{Launch}
(1 Week)
The first week of Semester 2 will be used to introduce and invite students to
the system, take registration, and randomly assign students to Group A or Group
B. The system will then become available to use in Week 2 of the semester.

\subsubsection{Results Analysis}
(4 Weeks)
Results analysis can begin during the data collection phase following launch.
Deliverables include:
\begin{itemize}
	\item Graphs of student engagement and progress, particularly comparisons
		between Group A and Group B.
	\item Graphs of student progress over the period.
	\item Correlation of student engagement and progress to personality types.
	\item Analysis of student opinions gathered through the rating system and
		how these compare to their measured engagement.
	\item Seek other interesting patterns in usage.
\end{itemize}

\subsubsection{Final Thesis}
(3 Weeks)
When all results have been analysed, the project will be compiled into a final
thesis document reporting findings and conclusions of the project.
